Case study validations of automatic bullet matching

### 2018-10-23 index.Rmd
spelling check, grammar

\hh{The automatic matching algorithm is based on a random forest [@breiman], which has a built-in internal testing mechanism to prevent potential overfitting. Error rates reported by random forest algorithms are based on these internal test sets. However, there is some discussion on whether or in which situations these error rates are biased [@rfOver2; @rfOver]. 
Neither of these papers adresses another issue with internal test sets: internal test sets are constructed to have the same distribution as the training data (apart from sampling variability). For any machine learning method the true test comes with testing the performance of an algorithm on an external test data. Good performance (in terms of low error rates) on external test data validates a ML algorithm. External data allows an assessment of the algorithm's sensitivity to distributional changes.  Using performance on external test data also allows us to test limitations of the algorithm by going outside the parameters of the training data.  }

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44. This mislabelling has been corrected now.

@@

What we find in \autoref{fig:compare} is that neither of the measure fulfills both of the minimal requirements laid out above. Both measures fulfill (R1), i.e. all  scores  of  different-source pairs are lower than scores of same-source pairs for SAM scores based on cross-correlation and RF scores.
However, SAM scores based on the multivariate random forest score show better separation between same-source and different-source scores than SAM scores based on cross-correlation. This can be seen from the larger horizontal distance between the modes (peaks) of the density curves of RF based SAM scores compared to the cross-correlation SAM scores.

@@

There are several approaches for potential improvements: we can try to fine tune the matching algorithm to take make and model of the firearm and ammunition used into account or expand the trainings base of the algorithm to include a wider variety of makes and models. The downside of this is that we need to considerably expand the database used for training.

>>>>

\hh{The automatic matching algorithm is based on a random forest [@breiman], which has a built-in internal testing mechanism to prevent potential overfitting. Error rates reported by random forest algorithms are based on these internal test sets. However, there is some discussion on whether or in which situations these error rates are biased [@rfOver2; @rfOver]. 
Neither of these papers addresses another issue with internal test sets: internal test sets are constructed to have the same distribution as the training data (apart from sampling variability). For any machine learning method the true test comes with testing the performance of an algorithm on an external test data. Good performance (in terms of low error rates) on external test data validates a ML algorithm. External data allows an assessment of the algorithm's sensitivity to distributional changes.  Using performance on external test data also allows us to test limitations of the algorithm by going outside the parameters of the training data.  }

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44. This mis-labeling has been corrected now.

@@

What we find in \autoref{fig:compare} is that neither of the measures fulfill both of the minimal requirements laid out above. Both measures fulfill (R1), i.e. all  scores  of  different-source pairs are lower than scores of same-source pairs for SAM scores based on cross-correlation and RF scores.
However, SAM scores based on the multivariate random forest score show better separation between same-source and different-source scores than SAM scores based on cross-correlation. This can be seen from the larger horizontal distance between the modes (peaks) of the density curves of RF based SAM scores compared to the cross-correlation SAM scores.

@@

There are several approaches for potential improvements: we can try to fine tune the matching algorithm to take make and model of the firearm and ammunition used into account or expand the training base of the algorithm to include a wider variety of makes and models. The downside of this is that we need to considerably expand the database used for training.
